# Methods

## DEMs

DEMs were obtained for two small sample areas in South Australia:

* Bakara. An area in the Murray Mallee with jumbled dunes, east-west dunes and flat areas
* Woakwine. An area to the south of the Coorong in the southeast of South Australia. This area rises gently from a lake, to subtle hills through which a trench runs.

Both area have a mix of native vegetation and agricultural land.

Table \@ref(tab:DEMs) lists the available DEMs, include the 'short' name used throughout the document.

```{r DEMs}

  rasters %>%
    dplyr::left_join(luraster %>%
                       dplyr::select(-short)
                     ) %>%
    dplyr::arrange(area, short) %>%
    dplyr::mutate(reference = as.logical(ref_flag)
                  , short = paste0("["
                                   , short
                                   , "]("
                                   , source
                                   , ")"
                                   )
                  ) %>%
    dplyr::select(area
                  #, file = name
                  , `short name` = short
                  , reference
                  , `original resolution (cm)` = original_cm
                  , licence
                  ) %>%
    kableExtra::kable(caption = paste0("Sample DEMs")
                      , format.args = list(digits = 2)
                      ) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))


```


## Processing

For each DEM, the following processing was applied:

* reprojected into GDA 2020
* masked to the minimum available overlap between all DEMs (in each area)
* aggregated or disaggregated to roughly 10 m from original resolution
* reprojected into the same `r terra::res(samples$ras[[1]])[1]` m raster
* generation of derived rasters via:
    + `Qfit` function in the `MultiscaleDTM` package `r envReport::cite_package("MultiscaleDTM")` using `v` argument (window size): `r windows$window %>% envFunc::vec_to_sentence()` cells
    + `land_class` function in the`envRaster` package `r envReport::cite_package("envRaster")` using `r windows$window %>% envFunc::vec_to_sentence()` cells for the small window and `r windows$window * 3` cells for the large window as input to the 10 class landscape classification
* sample of the derived rasters `r settings$sample_n` times to generate a range of visualisations and summary statistics.
    
The `Qfit` function generates several continuous and one categorical variable for a digital terrain model:

* `r paste0(as.character(formals(MultiscaleDTM::Qfit)$metrics)[-1], collapse = "\n* ")``

A [shiny app](https://ailich.shinyapps.io/Terrain_Attributes_Explorer_App/) is available to investigate the meaning of each of these variables.f

## Workflow

The data import, cleaning, analysis and report writing were done in a scripted workflow using the programs `R` and 'R-studio Desktop'. [`R`](https://www.r-project.org/) [@R-base] is an open source software environment for statistical computing and graphics. Base R can be extended via a range of open source packages to enable specific tasks or analyses. The packages used to produce this report are listed in Table \@ref(tab:packages).

[R-studio Desktop](https://posit.co/download/rstudio-desktop/) is a set of open source tools built to facilitate interaction with `R`.

```{r packages}

  knitr::kable(tibble::tibble(package = packages) %>%
                 dplyr::mutate(citation = paste0("@R-"
                                                 , package
                                                 )
                               ) %>%
                 dplyr::left_join(tibble::as_tibble(devtools::session_info(include_base = TRUE)$packages)) %>%
                 dplyr::select(package
                               , citation
                               , loadedversion
                               , date
                               , source
                               )
               , caption = "R [@R-base] packages used in the production of this report"
               )

```
