
```{r thisOne{{cont_metricID}}{{areaID}}}

  cont_metricID <- "{{cont_metricID}}"

```

### `r cont_metricID`

Figure \@ref(fig:raw{{cont_metricID}}{{areaID}}) shows rasters for `r cont_metricID` and each window size in the `r areaID` sample area.

Table \@ref(fig:contFig{{cont_metricID}}{{areaID}}) shows boxplots for each decile of `r cont_metricID`, allowing a comparison of values within each DEM across different ranges of `r cont_metricID`. Deciles are based on the values in the reference DEM: `r rasters$short[rasters$area == areaID & rasters$ref_flag == 1]`.

Figure \@ref(fig:plot{{cont_metricID}}{{areaID}}) shows the a distribution of values for each sample DEM and window size.

Figure \@ref(fig:diffPlot{{cont_metricID}}{{areaID}}) shows the distribution of differences between the reference DEM and the other DEMs (and window size).

```{r raw{{cont_metricID}}{{areaID}}, fig.height = 10, fig.cap = paste0(cont_metricID, " raster for each sample DEM and window size")}

  dems <- terr %>%
    dplyr::filter(area == areaID) %>%
    dplyr::mutate("{cont_metricID}" := purrr::map(terr
                                                  , tidyterra::select
                                                  , matches(cont_metricID)
                                                  )
                  , "{cont_metricID}" := purrr::map2(!!rlang::ensym(cont_metricID)
                                                     , bbox
                                                     , terra::crop
                                                     )
                  )
  
  tm_shape(terra::rast(dems[cont_metricID][[1]]) %>%
             setNames(paste0(dems$short, " ", dems$window))
           ) +
    tm_raster(n = 10
              , style = "quantile"
              ) +
    tm_facets(ncol = 2) +
    tm_layout(legend.outside = TRUE
              , legend.outside.position = "right"
              , legend.position = c(0.25, 0.25)
              )
  
```

<br>

```{r contFig{{cont_metricID}}{{areaID}}, fig.height = 10, fig.cap = "Boxplots within deciles for each sample DEM and window size"}

  reference <- rasters %>%
    dplyr::filter(area == areaID) %>%
    dplyr::pull(short) %>%
    `[[`(1) %>%
    as.character()

  cont_area %>%
    dplyr::filter(metric == cont_metricID) %>%
    dplyr::select(!contains("plot")) %>%
    tidyr::unnest(cols = c(data)) %>%
    dplyr::group_by(ID) %>%
    dplyr::filter(!is.na(value)) %>%
    dplyr::ungroup() %>%
    dplyr::select(area, metric, short, window, value, ID) %>%
    tidyr::pivot_wider(names_from = short
                       , values_from = value
                       ) %>%
    dplyr::mutate(cut_class = cut(!!rlang::ensym(reference)
                                  , breaks = quantile(!!rlang::ensym(reference)
                                                      , probs = seq(0, 1, 0.1)
                                                      , na.rm = TRUE
                                                      )
                                  , include.lowest = TRUE
                                  )
                  ) %>%
    tidyr::pivot_longer(tidyselect::any_of(as.character(rasters$short))
                        , names_to = "short"
                        ) %>%
    dplyr::mutate(short = factor(short, levels = levels(rasters$short))) %>%
    ggplot(aes(value, cut_class, fill = cut_class)) +
      geom_boxplot() +
      facet_grid(short ~ window
                 , scales = "free_y"
                 ) +
      scale_fill_viridis_d() +
      labs(title = cont_metricID
           , y = paste0(reference, " deciles")
           , fill = "deciles"
           ) +
      guides(fill = guide_legend(reverse = TRUE)) +
      theme(axis.text.y = element_blank())

  # ggplot(temp, aes(x = short
  #                  , xend = short
  #                  , y = q50
  #                  )
  #        ) +
  #   geom_segment(aes(y = q01
  #                    , yend = q99
  #                    )
  #                , size = 1
  #                , alpha = 0.5
  #                ) +
  #   geom_segment(aes(y = q10
  #                    , yend = q90
  #                    )
  #                , size = 2
  #                , alpha = 0.5
  #                ) +
  #   geom_segment(aes(y = q25
  #                    , yend = q75
  #                    )
  #                , size = 3
  #                , alpha = 0.5
  #                ) +
  #   geom_point(colour = "blue") +
  #   coord_flip() +
  #   facet_grid(window ~ .) +
  #   labs(title = cont_metricID
  #        , x = "value"
  #        , y = "Sample DEM"
  #        )

```

<br>

```{r plot{{cont_metricID}}{{areaID}}, fig.cap = paste0(cont_metricID, " results for the each DEM covering the sample area. Two window sizes were used to generate results")}

  cont_area %>%
    dplyr::filter(metric == cont_metricID) %>%
    dplyr::pull(plot) %>%
    `[[`(1)

```

<br>

```{r diffPlot{{cont_metricID}}{{areaID}}, fig.cap = paste0(cont_metricID, " difference between the best available (reference) DEM and each individual DEM for the ", settings$area, " sample area. Two window sizes were used to generate results")}

  cont_area %>%
    dplyr::filter(metric == cont_metricID) %>%
    dplyr::pull(diff_plot) %>%
    `[[`(1)

```
